%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}
% fixed width
\usepackage[scale=0.90,lf]{FiraMono}
% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge Md. Jubayer Hossain} \\ \vspace{5pt} 
    % Email
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{\url{b150605021@mib.jnu.ac.bd}} $|$
    % Linkedin
	\hspace{1pt} \faLinkedin \hspace{2pt} \texttt{\href{https://www.linkedin.com/in/jubayer28/}{JHossain}} 
    \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{\href{https://github.com/hossainlab}{hossainlab}} \hspace{1pt} $|$
    \hspace{1pt} \faGlobe \hspace{2pt}\texttt{\href{https://jhossain.netlify.app/}{Website}}
    \\ \vspace{-3pt}
\end{center}

%-----------EDUCATION-----------
\section{Academic Credentials}
\resumeSubHeadingListStart
% Bachelor 
\resumeSubheading
{Bachelor of Science in Microbiology}{Jan. 2016 -- Jan. 2019}
{Jagannath University}{Dhaka, Bangladesh}
%\resumeItemListStart
%\resumeItem {\textbf{Coursework}: Biostatistics, Public Health and Hygiene,  Bioinformatics-I, Bioinformatics-II}
%\resumeItem 
%{\textbf{Project}: Bioinformatics Approach for Profiling Antibiotic Resistance genes from Metagenomic DNA Sequence. \href{https://github.com/hossainlab/ARGs}{\myuline{Github}}}
%\resumeItemListEnd

% Masters 
\resumeSubheading
{Master of Science in Microbiology}{Jan. 2020 -- Present}
{Jagannath University}{Dhaka, Bangladesh}
\resumeSubHeadingListEnd


% Research 
\section{Working Papers}
\resumeItemListStart
\resumeItem{\textit{Syeda Tasneem Towhid, Ph.D, Md. Jubayer Hossain, Sumona Akter, Md. Atik Shariar Sammo;} \textbf{Perception of Students on Antibiotic Resistance and Prevention: An Online,Community-Based Case Study from Dhaka,Bangladesh}}

\resumeItem{\textit{Syeda Tasneem Towhid, Ph.D, Md. Jubayer Hossain, Sumona Akter, Tilottoma Roy, Muhibullah Shahjahan, Tanjum Ahmed Nodee, Bithi Akter;} \textbf{Self Management And Knowledge of Diabetic Patients in Bangladesh and the Prevalence rate of Diabetes}}


\resumeItem{\textit{Md.Ariful Islam, Ph.D, Md. Jubayer Hossain, Rubaiya Gulshan, Sumaiya Akter Mukta, Md. Sharif Miah;} \textbf{Knowledge and Attitudes of Thalassemia among Public University Students in Bangladesh}}

\resumeItem{\textit{Md. Ariful Islam, Ph.D, Md. Jubayer Hossain, Rubaiya Gulshan, Sumaiya Akter Mukta, Md. Sharif Miah, Md. Wahidul Islam;} \textbf{Quality of Life among Bangladeshi Patients with Thalassemia using the SF-36 Questionnaire}}

\resumeItem{\textit{Dr. Md. Kamrujjaman, Alamgir Hossain Tanjim, Md. Jubayer Hossain;} \textbf{General Concept of Diabetes among Villagers of Different Districts in Bangladesh: A Cross-sectional Study}}


\resumeItem{\textit{Sabia Sultana, Md. Jubayer Hossain, Atik Shahriar Sammo, Bithi Akter, Tanjum Ahmed Nodee, Sanjida Akter Sathy, Ema Akter, Susmita Jahan Bristy;} \textbf{ Perception and the Impact of Distance Learning on Students from the Science Faculty at Jagannath University, Dhaka during COVID-19: An Exploratory Study}}
\resumeItemListEnd



%-----------PROJECTS-----------
\section{Projects}
\resumeItemListStart
\resumeItem{Heart Disease Analysis and Prediction Using Machine Learning. \href{https://github.com/hossainlab/Heart_Study}{\myuline{[Github]}}}

\resumeItem{Calories Burn Prediction using Machine Learning. \href{https://github.com/hossainlab/Calories_Burnt}{\myuline{[Github]}}}

\resumeItem{Hepatitis Mortality Prediction using Machine Learning. \href{https://github.com/hossainlab/Hepatitis_Mortality}{\myuline{[Github]}}}

\resumeItem{Soaking temperature affected the length increase in beans (\textit{Phaseolus vulgaris}) when they were soaked in water for 12 hours. \href{https://github.com/hossainlab/Hepatitis_Mortality}{\myuline{[Github]}}}

\resumeItemListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}]
	\small{\item{
			\textbf{Programming Languages:} {Python, R, SQL, Julia, JavaScript}\vspace{2pt} \\ 
			\textbf{Tools \& Softwares:} {SPSS, Microsoft Excel, Github, \LaTeX, KoboToolBox, Mendley, Turnitin}
			
	}}
\end{itemize}



% Teaching 
\section{Teaching}
\resumeSubHeadingListStart
% Bachelor 
\resumeSubheading
{Introduction to Scientific Computing for Biologist}{Nov. 2020 -- Jan. 2021}
{\href{https://chiralbd.netlify.app/teaching/scb/}{\myuline{Course Website}}}{Lead Organizer \& Instructor}
\resumeItemListStart
\resumeItem {Fundamental course on scientific computing for biologists. I taught Fundamentals of Biostatistics, Python, R Programming, Bioconductor, UNIX, Git, Github, and \LaTeX}
\resumeItemListEnd
 
\resumeSubheading
{Python for Health Data Analytics}{July 2021 -- July 2021}
{\href{https://chiralbd.netlify.app/teaching/py4hda/}{\myuline{Course Website}}}{Lead Organizer \& Instructor}
\resumeItemListStart
\resumeItem {Fundamentals course on health data analytics including data collection, data cleaning, data visualization, linear regression and logistic regression model building using Python.}
\resumeItemListEnd

\resumeSubheading
{Health Research ToolBox -- A step by step guide for beginners}{Start on December 2021}
{\href{https://chiralbd.netlify.app/teaching/research-toolbox/program-intro/}{\myuline{Course Website}}}{Lead Organizer \& Instructor}
\resumeItemListStart
\resumeItem {Fundamentals course on health data analytics including data collection, data cleaning, data visualization, linear regression and logistic regression model building using Python.}
\resumeItemListEnd
\resumeSubHeadingListEnd


% Teaching 
\section{Affiliations}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://chiralbd.netlify.app/}{Center for Health Innovation, Research, Action, and Learning --Bangladesh}}{June 2020 -- Present}
{Founder \& Management Lead}{}
\resumeItemListStart
\resumeItem{The main focus of this group is to solve healthcare problems with the help  of data in Bangladesh. The primary responsibilities include designing courses, data analysis, and team management.}
\resumeItemListEnd


\resumeSubheading
{\href{https://chiralbd.netlify.app/}{Whitehope Academy}}{July 2016 -- June 2020}
{Instructor}{}
\resumeItemListStart
\resumeItem{I provided comprehensive tutoring in Physics and Chemistry to the students of 10th, 11th, and 12th grade.}
\resumeItemListEnd

\resumeSubheading
{\href{https://chiralbd.netlify.app/}{Bio-Bio-1}}{July 2017 -- Present}
{Team Member}{}
\resumeItemListStart
\resumeItem{I was an active participant in their weekly study circle and learned a lot from them; especially, I learned bioinformatics techniques with the help of Python.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section{References}
\begin{tabular}{lr}
	% Referee 1
	\begin{minipage}[t]{3in}
		\textbf{Syeda Tasneem Towhid, Ph.D}\\
		\textit{Assistant Professor \\ Department of Microbiology }\\
		Jagannath University, Dhaka-1100\\
		\Letter\ \href{mailto:towhidst@mib.jnu.ac.bd}{towhidst@mib.jnu.ac.bd}
	\end{minipage}
	&
	% Referee 2
	\begin{minipage}[t]{3in}
		\textbf{Mohammad Ariful Islam, Ph.D}\\
		\textit{Associate Professor \\ Department of Microbiology }\\
		Jagannath University, Dhaka-1100\\
		\Letter\ \href{mailto:ariful@mib.jnu.ac.bd}{ariful@mib.jnu.ac.bd}
	\end{minipage}
	
	\\
\end{tabular}
%-------------------------------------------
\end{document}
